Initial Analysis

### 2020-07-31 Scripts/Initial_Analysis.Rmd
Re plotted all figures (all ist gut!)

  Rev_Plot <- ggplot(
    # Regional plots
    data = Subregion_Rev_Data,
    aes(
      x=reorder(id,Value_sum),
      y=Value_sum, 
      fill=Value_sum
    )
  ) +    
    ylim(-1500, max_Rev_lim) +
    geom_bar(stat="identity") +
    # Regional averages
    geom_point(data = Subregion_Rev_Data,
               aes(
                 x=reorder(id,Value_sum),
                 y=Value_m
               ),
               colour = "black",
               alpha = 0.5
    ) +
    # Regional sds
    geom_errorbar(data = Subregion_Rev_Data,
                  aes(
                    ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd), # sets lower to 0
                    ymax=Value_m+Value_sd
                  ), 
                  width=.2,
                  position=position_dodge(.9),
                  alpha = 0.5) +
    # Looking good
    theme_minimal() +
    theme(
      legend.position = c(0.73,0.60),
      axis.text = element_blank(),
      axis.title = element_blank(),
      panel.grid = element_blank(),
      plot.margin = margin(0,-10,-6,-10,"cm")
    )  +
    # Base line
    # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
    #              colour = "black", size=0.1, inherit.aes = FALSE) +
    coord_polar(start = 0) + 
    geom_text(data=label_data_rev, 
              aes(x=id,
                  y=Value_sum,
                  label=sub_region,
                  hjust=hjust), 
              color="black",
              fontface="bold",
              size=2, 
              angle= label_data_rev$angleb, 
              inherit.aes = FALSE) +
    scale_fill_gradientn("",
                         colours = pal,
                         limits = c(0,14000),
                         breaks = seq(0,14000,3500)
                         ) +
    guides(fill = guide_colorbar(label.position = "left")
    );Rev_Plot

@@

# Conuntry Names relation

matching_country_names <- my_path("D","Spatial","matching_names.csv", read = T) %>%
  mutate(eez_name = ifelse(is.na(eez_name),sf_eez_name,eez_name))

# Spatial Data needed to remove duplicates
# sau_eez_fes <- fread(paste(my_path("G"),"Spatial/SAU/sau_eez_fes.csv",sep="")) %>% 
  # clean_names()

# New dara produced by Vicky 
sau_eez_fes <- read_excel("~/Desktop/EEZ_FishingEntityID_v2_9June2020.xlsx")

Clean_sau_eez_fes <- sau_eez_fes

@@

# View(unique(World_land_sf$fishing_entity))

# head(World_land_sf)

@@

# Regional UN-sub region area
Regional_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_sau_eez_fes) %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
  group_by(sub_region) %>% 
  summarise(Size_Region = sum(Area_km2)) %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  arrange(sub_region)

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(eez_name=territory) #%>% 
  # mutate(eez_name = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",eez_name)
         # )

@@

Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
  mutate(eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                           ifelse(eez_name == "Curacao (Netherlands)","Curaçao (Netherlands)",eez_name)
  ),
  fishing_entity = ifelse(fishing_entity == "Cote dIvoire","Côte d'Ivoire",
                          ifelse(fishing_entity == "Curacao (Netherlands)","Curaçao (Netherlands)",
                                 ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)","Spain",fishing_entity)))
  )

@@

Tresholded_T_Data <- Clean_Results_Trans %>% 
  filter(
    area_index >= Min_AI,
    area_index <= Max_AI,
    model_index >= MI
  )

@@

```{r test, eval = F, echo = F}

Tra <- Summary_Trans %>% 
  mutate(Type = "Trans")

Dis <- Summary_Discrete %>% 
  mutate(Type = "Dis")

Solo <- Summary_Discrete_Exclusive %>% 
  mutate(Type = "Solo")

All <- bind_rows(Tra,Dis,Solo) %>% 
  select(1:7) %>% 
  group_by(taxon_key,fishing_entity) %>% 
  summarise(n())

missing <- anti_join(Total_SAU_Sampled,All,
          by = c("fishing_entity_id","taxon_key"))

missing %>% 
  group_by(Variable) %>% 
  summarise(sum(Value))

# Now
58242635
# Goal
58986239

58986239-58242635

@@

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  left_join(EEZ_Area, 
            by = "eez_name") %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    # Weight_Bins = cut(Weight_Spp,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                           labels = c('super low', 'low','median', 'high','super high')
    )
  )

@@

Value_Trans_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  # left_join(Entity_Area,
  #           by = "fishing_entity") %>%
  # # Include the weighted method for supplementals
  # mutate_at(
  #   vars(catch,value),
  #   funs(weight= ./(Size_Entity/1000000))
  # ) %>%
  # gather("Variable","Value",catch:value,catch_weight:value_weight) %>%
  gather("Variable","Value",catch:value) %>%
  group_by(fishing_entity,Variable,Value) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_EEZ,
            by = c("fishing_entity", "Variable") 
            ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )

@@

# Transboundary Species shapefile
World_sf_si <- World_sf %>%
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="eez_name") %>% 
  st_transform(crs = "+proj=eck4")
  # st_transform(crs = 4326)

@@

```{r Figure_1}

# Set color pal
pal <- wes_palette("Zissou1",100,type = "continuous")

# Variable to plot (value or catch)
Variable_plot <- "value"
CreateFigureOne(Variable_plot)

@@

# -------------------------- #
# Transboundary data
# -------------------------- #

# Stock status Data

Status_Data_Plot <- Tresholded_T_Data %>% 
  left_join(Status_Data, 
            by =c("eez_name","taxon_key")
  ) %>%
  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
  group_by(fishing_entity,status) %>% 
  summarise(value = length(unique(taxon_key))) %>% 
  left_join(UN_Regions, by ="fishing_entity") %>%
  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  mutate(value = ifelse(value > 100,100,value)) %>% 
  filter(!is.na(fishing_entity),
         !str_detect(fishing_entity, ".\\(.") # remove associated territories
  ) %>% 
  select(individual = fishing_entity,observation = status,group = Georegion,value) %>% 
  arrange(group,value) %>% 
  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value),
         observation = ifelse(observation %in% c("Developing","Rebuilding"),"Category A",
                              ifelse(observation == "Max Exploited","Category B",
                                     ifelse(observation %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
                              )
         )
  ) %>% 
  group_by(individual,observation,group) %>% 
  summarise(value = sum(value))

Status_Plot_Data <- tibble(
  fishing_entity = rep(unique(Status_Data_Plot$individual),4),
  observation = rep(unique(Status_Data_Plot$observation),153)
) %>% 
  left_join(UN_Regions) %>% 
  rename(individual = fishing_entity) %>% 
  full_join(Status_Data_Plot,
            by = c("individual","observation")
  ) %>% 
  mutate(value = ifelse(is.na(value),0,
                        ifelse(value < -100,-100, # if less than 100, 100
                               ifelse(value > 100,100, # if more than 100, 100
                                      value)
                        )#, # Ser NAs to 0's
                        # group = ifelse(is.na(group),"Other",group)
  )
  ) %>% 
  select(individual,observation,group=georegion,value) %>% 
  filter(group != "other")

@@

# Get the name and the y position of each label
label_data <- Status_Plot_Data %>% 
  # filter(value > 0) %>% 
  group_by(id, individual) %>% 
  summarize(tot=sum(value,na.rm=T)) %>% 
  mutate(
    individual = ifelse(individual == "Saint Vincent & the Grenadines","Snt. Vincent & Grenadines", individual)
    )

@@

# If you want to show revenue
# Country_Spp_Data <- sau_eez_fes %>% 
#   group_by(fishing_entity_id,fishing_entity) %>% 
#   summarise(n=n()) %>% 
#   select(-n) %>% 
#   left_join(SAU_Revenue_Data) %>% 
#   left_join(Tresholded_T_Data) %>% 
#   left_join(Exploited_Species) %>% 
#   left_join(Top_5_Ecosystem) %>% # includes the groups
#   filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>% 
#   group_by(fishing_entity,group) %>% 
#   summarise(top_catch = sum(mean_value)/1000000) %>%  # Million
#   group_by(group) %>% 
#   top_n(5)

# If you want to show catch  
Country_Spp_Data <- Tresholded_T_Data %>%
  left_join(Exploited_Species) %>%
  left_join(Top_5_Ecosystem) %>% # includes the groups
  left_join(Clean_sau_eez_fes) %>% 
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")
  ) %>%
  filter(taxon_name %in% Top_5_Ecosystem$taxon_name,
         Variable == "catch") %>%
  group_by(fishing_entity,group) %>%
  summarise(top_catch = sum(Value)) %>%
  group_by(group) %>%
  top_n(5) %>% 
  mutate(
    fishing_entity = ifelse(fishing_entity == "Korea (South)", "S. Korea",
                            ifelse(fishing_entity == "Russian Federation","Russia",
                                   ifelse(fishing_entity == "Papua New Guinea", "N.Guinea",
                                          ifelse(fishing_entity == "Solomon Isl.", "Solomon",fishing_entity)))
    )
  )

@@

Median_trans <- median(Species_Data$value)
# hist(Species_Data$value)
# unique(Species_Data$group)

@@

  # geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") + # All groups median

>>>>

  Rev_Plot <- ggplot(
    # Regional plots
    data = Subregion_Rev_Data,
    aes(
      x=reorder(id,Value_sum),
      y=Value_sum, 
      fill=Value_sum
    )
  ) +    
    ylim(-1500, max_Rev_lim) +
    geom_bar(stat="identity") +
    # Regional averages
    geom_point(data = Subregion_Rev_Data,
               aes(
                 x=reorder(id,Value_sum),
                 y=Value_m
               ),
               colour = "black",
               alpha = 0.5
    ) +
    # Regional sds
    geom_errorbar(data = Subregion_Rev_Data,
                  aes(
                    ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd), # sets lower to 0
                    ymax=Value_m+Value_sd
                  ), 
                  width=.2,
                  position=position_dodge(.9),
                  alpha = 0.5) +
    # Looking good
    theme_minimal() +
    theme(
      legend.position = c(0.73,0.60),
      axis.text = element_blank(),
      axis.title = element_blank(),
      panel.grid = element_blank(),
      plot.margin = margin(0,-10,-6,-10,"cm")
    )  +
    # Base line
    # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
    #              colour = "black", size=0.1, inherit.aes = FALSE) +
    coord_polar(start = 0) + 
    geom_text(data=label_data_rev, 
              aes(x=id,
                  y=Value_sum,
                  label=sub_region,
                  hjust=hjust), 
              color="black",
              fontface="bold",
              size=2, 
              angle= label_data_rev$angleb, 
              inherit.aes = FALSE) +
    scale_fill_gradientn("",
                         colours = pal,
                         limits = c(0,14100),
                         breaks = seq(0,14000,3500)
                         ) +
    guides(fill = guide_colorbar(label.position = "left")
    );Rev_Plot

@@

# New dara produced by Vicky 
Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)

@@

@@

# Regional UN-sub region area
Regional_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_sau_eez_fes) %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity_id %in% Clean_sau_eez_fes$fishing_entity_id) %>% 
  group_by(sub_region) %>% 
  summarise(Size_Region = sum(Area_km2,na.rm=T)) %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  arrange(sub_region)

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(eez_name=territory) %>% 
  mutate(
    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
    eez_name = gsub("Chile","Chile (mainland)",eez_name),
    eez_name = gsub("Curaçao","Curacao",eez_name),
    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
    eez_name = gsub("Vietnam","Viet Nam",eez_name),
    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
                             ifelse(eez_name == "Greece","Greece (without Crete)",
                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
                                                  ifelse(eez_name == "Italy","Italy (mainland)",
                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
                                                                                     ifelse(eez_name =="Spain (Mediterranean and Gulf of Cadiz)","Spain (mainland, Med and Gulf of Cadiz)",
                                                                                            ifelse(eez_name =="Réunion (France)","Reunion (France)",
                                                                                     eez_name)
                                                                       ))
                                                                       )
                                                         ))))
                             )
                      )
    )))

@@

Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
  mutate(
    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
    eez_name = gsub("Chile","Chile (mainland)",eez_name),
    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
    eez_name = gsub("Vietnam","Viet Nam",eez_name),
    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
                             ifelse(eez_name == "Greece","Greece (without Crete)",
                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
                                                  ifelse(eez_name == "Italy","Italy (mainland)",
                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
                                                                                     eez_name)
                                                                       ))
                                                         ))))
                             )
                      )
    )

Clean_Results_Trans %>% anti_join(Clean_sau_eez_fes, by = "eez_name") %>% 
  group_by(eez_name) %>% 
  summarise(n())

@@

Tresholded_T_Data <- Clean_Results_Trans %>% 
  filter(
    area_index >= Min_AI,
    area_index <= Max_AI,
    model_index >= MI
  ) %>% 
  select(-fishing_entity) %>% 
  left_join(Clean_sau_eez_fes, by = "eez_name")

@@

@@

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_id) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  # left_join(EEZ_Area, 
  #           by = "eez_name") %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    # Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    # Weight_Bins = cut(Weight_Spp,breaks = 5),
    # Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                           # labels = c('super low', 'low','median', 'high','super high')
    # )
  )

@@

Value_Trans_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = c("fishing_entity","fishing_entity_id")
            ) %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  # left_join(Entity_Area,
  #           by = "fishing_entity") %>%
  # # Include the weighted method for supplementals
  # mutate_at(
  #   vars(catch,value),
  #   funs(weight= ./(Size_Entity/1000000))
  # ) %>%
  # gather("Variable","Value",catch:value,catch_weight:value_weight) %>%
  gather("Variable","Value",catch:value) %>%
  group_by(fishing_entity,Variable,Value) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_EEZ,
            by = c("fishing_entity", "Variable") 
            ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )

@@

# Transboundary Species shapefile
World_sf_si <- World_sf %>%
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="eez_id") %>% 
  st_transform(crs = "+proj=eck4")
  # st_transform(crs = 4326)

Transboundary_Spp %>% anti_join(World_sf, by = "eez_id")

@@

```{r Figure_1}
gc()
# Set color pal
pal <- wes_palette("Zissou1",100,type = "continuous")

# Variable to plot (value or catch)
Variable_plot <- "catch"
CreateFigureOne(Variable_plot)

@@

# -------------------------- #
# Transboundary data
# -------------------------- #
# Stock status Data
Status_Data_Plot <- Tresholded_T_Data %>% 
  left_join(Status_Data, 
            by =c("eez_name","taxon_key")
  ) %>%
  mutate(status = ifelse(is.na(status),"No Status",status)) %>% 
  group_by(fishing_entity,status) %>% 
  summarise(value = length(unique(taxon_key))) %>% 
  left_join(UN_Regions, by ="fishing_entity") %>%
  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  mutate(value = ifelse(value > 100,100,value)) %>% 
  filter(!is.na(fishing_entity),
         !str_detect(fishing_entity, ".\\(.") # remove associated territories
  ) %>% 
  select(individual = fishing_entity,observation = status,group = Georegion,value) %>% 
  arrange(group,value) %>% 
  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value),
         observation = ifelse(observation %in% c("Developing","Rebuilding"),"Category A",
                              ifelse(observation == "Max Exploited","Category B",
                                     ifelse(observation %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
                              )
         )
  ) %>% 
  group_by(individual,observation,group) %>% 
  summarise(value = sum(value))

length(unique(Status_Data_Plot$individual))
length(unique(Status_Data_Plot$observation))

Status_Plot_Data <- tibble(
  fishing_entity = rep(unique(Status_Data_Plot$individual),4),
  observation = rep(unique(Status_Data_Plot$observation),157)
) %>% 
  left_join(UN_Regions) %>% 
  rename(individual = fishing_entity) %>% 
  full_join(Status_Data_Plot,
            by = c("individual","observation")
  ) %>% 
  mutate(value = ifelse(is.na(value),0,
                        ifelse(value < -100,-100, # if less than 100, 100
                               ifelse(value > 100,100, # if more than 100, 100
                                      value)
                        )#, # Ser NAs to 0's
                        # group = ifelse(is.na(group),"Other",group)
  )
  ) %>% 
  select(individual,observation,group=georegion,value) %>% 
  filter(group != "other")

@@

# Get the name and the y position of each label
label_data <- Status_Plot_Data %>% 
  # filter(value > 0) %>% 
  group_by(id, individual) %>% 
  summarize(tot=sum(value,na.rm=T)) %>% 
  mutate(
    individual = ifelse(individual == "Saint Vincent & the Grenadines","Snt. Vincent & Grenadines",
                        ifelse(individual == "Brunei Darussalam","Burnei",
                               individual)
                        )
  )

@@

# Just catch data
Catch_Data <- SAU_Sampled_Data %>% 
  filter(Variable == "catch")

# Just country names
country_names <- Clean_sau_eez_fes %>% 
  select(fishing_entity,fishing_entity_id) %>% 
  distinct()

# If you want to show catch  
Country_Spp_Data <- Tresholded_T_Data %>%
  left_join(Exploited_Species) %>%
  left_join(Top_5_Ecosystem) %>% # includes the groups
  group_by(taxon_key,taxon_name,fishing_entity_id,fishing_entity,group) %>%
  summarise(n()) %>% 
  left_join(Catch_Data,
            by = c("fishing_entity_id","taxon_key")
  ) %>%
  filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>%
  group_by(fishing_entity_id,group) %>%
  summarise(top_catch = sum(Value,na.rm=T)) %>%
  group_by(group) %>%
  top_n(5) %>% 
  left_join(country_names, by = "fishing_entity_id") %>% 
  mutate(
    fishing_entity = ifelse(fishing_entity == "Korea (South)", "S. Korea",
                            ifelse(fishing_entity == "Russian Federation","Russia",
                                   ifelse(fishing_entity == "Papua New Guinea", "N.Guinea",
                                          ifelse(fishing_entity == "Solomon Isl.", "Solomon",fishing_entity)))
    )
  )

@@

@@
